Missing data: Current practice in football research and recommendations for improvement

### 2020-10-15 paper/paper.Rmd

```{r libraries, message = FALSE}
library(tidyverse)
library(naniar)
library(visdat)
library(patchwork)
library(fitzRoy)
library(mice)
library(truncnorm)
library(janitor)
library(cowplot)
```

>>>>

```{r libraries, message = FALSE}
library(tidyverse)
library(naniar)
library(visdat)
library(patchwork)
library(fitzRoy)
library(mice)
library(truncnorm)
library(janitor)
library(drake)
library(cowplot)
```

```{r load-funs}
pivot_var <- function(data, var){
  data %>% 
    select(title,
           reviewer,
           {{ var }}) %>% 
    pivot_wider(names_from = reviewer,
                values_from = {{ var }})
}

agree_var <- function(data, var){
  statement_agree <- pivot_var(data, {{ var }}) %>% 
    select(reviewer_1, reviewer_2) %>% 
    irr::agree()

  statement_agree$value
}

```{r read-data}
gs_football <- readr::read_rds(here::here("data",
                           "gs-football.rds"))
```

```{r load-drake}
# loadd()
```
